Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-05-25 scnn.tex
abstract

	\todo{(Michaël) I would not invent a new term, SCNN, but rather say that convolutional neural networks on graphs (or GCNs) can be efficiently applied to (spherical?) cosmological applications.
	Arguments: the method is not new and hence don't deserve a new name. Emphasize that it is generic to the data structure, and that the sphere is simply a particular graph.
	Ideas: Graph Convolutional Networks for efficient spherical ???, Efficient spherical ??? with GCNs and Healpix sampling
    We make the code publicly available.
}

>>>>

Convolutional Neural Networks (CNNs) are becoming an important analysis tool in cosmology and astrophysics.
In many applications, the data comes in a form of spherical maps.
A popular format for these maps is Healpix, which uses equal-area, isolatitude sampling.
We present a CNNs for analysis of full- and partial sky Healpix maps, which we call HealpixCNN (???).
This approach is based on representing a sphere as a graph of connected nodes.
We describe a convolution operation defined on that graph.
HealpixCNN (???) uses Tensorflow as the underlying engine and can utilise most of it functionalities.
Architectures can be designed in a similar way as standard CNNs used for image analysis.
We find that the graph-based convolution is very efficient (MORE HERE)..
The filters learned by the HealpixCNN are restricted to being radial.
We demonstrate the method on a simple classification problem of mass maps from two cosmological models.
We compare the performance to a simple benchmark classifier, which uses histograms of map pixel values.
HealpixCNN achieves much better testing accuracy than the benchmark approach.
We make the code and examples available to the public.

	\todo{(Michaël) I would not invent a new term, SCNN, but rather say that convolutional neural networks on graphs (or GCNs) can be efficiently applied to (spherical?) cosmological applications.
	Arguments: the method is not new and hence don't deserve a new name. Emphasize that it is generic to the data structure, and that the sphere is simply a particular graph.
	Ideas: Graph Convolutional Networks for efficient spherical ???, Efficient spherical ??? with GCNs and Healpix sampling
    We make the code publicly available.
    \\
    \todo{(Tomek) How about HealpixCNN? Or HealpixNet? Or HealNet?}

}
